---
title: 'Directed Study Assignment #2'
author: "Darius McDaniel"
date: "October 22, 2015"
output: word_document
---

## First Function


Given a  lat/lon pair and a distance in miles the functuon **myPWS** outputs three type of information: 

1) The url used to pull information from Wunderground.

2) The location (city, state and country).

3) A data frame with the nearby Personal Weather Stations that are less than the specified number of miles away. You may parse XML or JSON to get the job done. 

Here is the function and some examples:


```{r}

myPWS <- function(lat,lon,dist) {
  
  library(RJSONIO)
  library(RCurl)
  
  #Main part of api
  api <- paste("http://api.wunderground.com/api/b7dbd5ef0f04904b/geolookup/q/",sep="")

  #lat and lon combined
  latlon <- paste(lat,lon,sep = ",")

  url <- paste(api,latlon, ".json",sep = "")
  addr <- getURL(url)
  
  #JSON parsed
  url.json <- fromJSON(addr)
  
  #Used to count for correct parsing
  #str(url.json,2)
  
  
  #Gives parsed CITY,State and Country unlisted as data object
  unlist(url.json$location[6]) -> CITY 
  unlist(url.json$location[5]) -> STATE
  unlist(url.json$location[4]) -> COUNTRY
  
  #Below gives the Location for output
  Location <- paste(CITY,STATE,COUNTRY,sep = " ")
  
  #This gives us all personal weather stations data in area specified by lat and lon
  pws <- do.call(rbind,url.json$location$nearby_weather_stations$pws[[1]])
  pwsDF <- data.frame(pws)
 
  #Use dplyr for quick filter of the stations based in distance specified by user
  library(dplyr)
  
  stations_ <- pwsDF %>% 
    filter(distance_mi < dist) %>% 
    mutate(stations = id) %>%
    select(stations,neighborhood, distance_mi)
  
  stations1 <-list(stations_)
  stations <- do.call(rbind,stations1)

  #This returns url, location and station data for lat lon
  return(list(url=url,Location=Location,stations=stations))
 
 
  }
  
#QA

   myPWS(lat=33.79757,lon=-84.32332,dist=2) # 1518 Clifton Rd, Atl GA 30322
   myPWS(lat=-23.533333,lon=-46.616666,dist=3)   # Sao Paulo Brazil
   myPWS(lat=48.86666,lon=2.333333,dist=1)  # Paris, France
   myPWS(lat=42.3313889,lon=-83.045833,dist=5) # Detroit, Michigan
   myPWS(lat=40.714166,lon=-74.00638,dist=5) # New York, New York
  


```

## Second Function
Below is a function called **WeatherPWS**. This accepts a vector of station names as input from the function **myPWS**. 
For each station this function gives back basic weather information such as (name, weather, temp_f, wind_string, wind_mph, feelslike_f). 

Here is the function and some examples:

```{r}


getWeatherPWS <- function(stations) {
  library(RJSONIO)
  library(RCurl)
  
   masterlist <- list() # Blank master list
   jj = 1 # Counter for incrementing the masterlist
  

  for (ii in 1:length(stations)) {
    
    base_string <- "http://api.wunderground.com/api/b7dbd5ef0f04904b/forecast/geolookup/conditions/q/pws:" 
   
    urlPWS <- paste(base_string,stations[ii], ".json",sep = "")
    base_string_URL <- getURL(urlPWS)
    
    url.json <- fromJSON(base_string_URL)
    #str(url.json,2)
    
    #Gives parsed station_id, weather,temp_f, wind_string, wind_mph,feelslike_f and precip_daily_in  unlisted as data object
    unlist(url.json$current_observation$station_id) -> station_id 
    unlist(url.json$current_observation$weather) -> weather 
    unlist(url.json$current_observation$temp_f) -> temp_f
    unlist(url.json$current_observation$wind_string) -> wind_string
    unlist(url.json$current_observation$wind_mph) -> wind_mph
    unlist(url.json$current_observation$feelslike_f) -> feelslike_f
    unlist(url.json$current_observation$precip_today_in) -> precip_today_in
    
    masterlist[[jj]] <- list(station_id=station_id,weather=weather,temp_f=temp_f,wind_string=wind_string,wind_mph=wind_mph,feelslike_f=feelslike_f,precip_today_in=precip_today_in)
    jj = jj + 1
    
    
  }
   pws_weather <-  do.call(rbind,masterlist)
    return(pws_weather)
}
   
   
   
   myPWS(lat=33.79757,lon=-84.32332,dist=2)$stations$station[1:10] -> inputs 
   getWeatherPWS(inputs)


   myPWS(lat=40.714166,lon=-74.00638,dist=5)$stations$station -> inputs
   getWeatherPWS(inputs)

 

```

